---
title: "Binder Template"
author: "Markus Konkol"
licenses:
  code: Apache License 2.0
  data: CC0
  text: CC-BY-4.0
date: "25-3-2022"
output: html_document
abstract: "This repository serves as a template to start a reproducible computational analysis written in R, which will later run on mybinder."
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries
The following libraries are needed to run this file. 
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library("readr")
library("ggplot2")
library("weathermetrics")
```
readr by [@Wickham_readr]
ggplot2 by [@wickham_ggplot2]
weathermetrics by [@anderson]

## Load data
Load data from the data folder.
```{r, echo=TRUE, message=FALSE, warning=FALSE}
temperature <- read_delim("data/temperature.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
```

## Process data 
Convert from Celsius to Fahrenheit. Function is defined in the file functions.R and stored in the folder "code".
```{r}
source("code/functions.R")
temperature_F <- celsius.to.fahrenheit(temperature$temperature_C)
```

## Visualise data 
This code chunk visualises the data in a time series figure.
```{r, echo=TRUE, message=FALSE, warning=FALSE}
jpeg("figures/figure1.jpg", width = 350, height = 350)
p <- ggplot(temperature, aes(x=time, y=temperature_C)) +
  geom_line() + 
  xlab("")
dev.off()
p
```

## Getting references objects for references.bib file.

```{r}
citation("ggplot2")
```

## References